\chapter{Introduction}
\justify
\quad 


\section{Objectives}
\justify 
\quad 
VoIP (Voice over Internet Protocol) is the transmission of voice and multimedia
content over an internet connection . VoIP allows users to make voice calls from a computer, smartphone, other mobile devices, special VoIP phones and WebRTC-enabled browsers. VoIP is a technology useful for both consumers and businesses, as it typically includes other features that can't be found on common phone services. These features can include call recording , custom caller ID, or voicemail to e-mail. It is also helpful to organizations as a way to unify communications.
3 The process works similarly to a regular phone, but VoIP uses an internet connection instead of a telephone company's wiring. VoIP is enabled by a group of technologies and methodologies used to deliver voice communications over the internet , including enterprise local area networks or wide area networks.
A VoIP service will convert a user's voice from audio signals to digital data, then send that data through the internet. If another user is calling from a regular phone number, the signal is converted back to a telephone signal before it reaches that user. VoIP can also perform routing of incoming and outgoing calls through existing telephone networks. However, some VoIP services may only work over a computer or VoIP phone.


\section{Scope}
The following are the most basic VoIP call features. These features are provided by most VoIP service providers for free.
\begin{itemize}
\item \textbf{3-way calling} : Write description of the point here.
\item \textbf{411 directory assistance} : Write description of the point here.
\item \textbf{Auto forwarding} : Write description of the point here.
\item \textbf{Address book} : Write description of the point here.
\item \textbf{Call block, forward, and hold} : Write description of the point here.
\item \textbf{Bring Your Own Device} : Write description of the point here.
\item \textbf{Caller ID and ID block} : Write description of the point here.
\item \textbf{Number portability} : Write description of the point here.
\item \textbf{E911} : Write description of the point here.
\item \textbf{Call return and Call waiting (including with caller ID)} : Write description of the point here.
\item \textbf{Voicemail} : Write description of the point here.
\item \textbf{Speed dialling} : Write description of the point here.
\end{itemize}


\newpage


